Finiteness in Cubical Type Theory

### 2020-06-25 sections/search.tex
Update search.tex

These properties are closely related to the axiom of choice: in particular, the
statement that ``every type is omniscient'' implies the AOC. \todo{Reference for
this, and possible proof? Also it might not be entirely correct: I think you
need a truncation somewhere for omniscience to be equivalent to the AOC}
Because we're constructive, only a select few types are omniscient: finite
types, for instance (why finite types are omniscient is not too difficult to
see, but we will explain it soon).
Perhaps surprisingly, it is not \emph{only} finite types
which are exhaustible.
Certain infinite types can be
exhaustible~\cite{escardoInfiniteSetsThat2007}, but an exploration of that is
beyond the scope of this work.

@@

@@

Finally, we can get around the order requirement for prop-valued predicates for
omniscience.
\begin{lemma}
  Omniscience and exhaustibility coincide for prop-valued predicates.
\end{lemma}

\section{Countdown}
\section{Automating Proofs}
One use for above constructions is the automation of certain proofs.
In \cite{firsovDependentlyTypedProgramming2015}, which uses a similar approach
to ours, the \(\AgdaDatatype{Pauli}\) group is used as an example.
\ExecuteMetaData[agda/Data/Pauli.tex]{def}
As \(\AgdaDatatype{Pauli}\) has 4 constructors, \(n\)-ary functions on
\(\AgdaDatatype{Pauli}\) may require up to \(4^n\) cases, making even simple
proofs prohibitively verbose.

>>>>

Because we're constructive, only a select few types are omniscient: finite
types, for instance (the law of the excluded middle implies that all types are
omniscient, meaning that all types are omniscient classically).
Perhaps surprisingly, it is not \emph{only} finite types which are exhaustible.
Certain infinite types can be
exhaustible~\cite{escardoInfiniteSetsThat2007}, but an exploration of that is
beyond the scope of this work.

@@

\begin{lemma}
  If exhaustibility implies omniscience, then the axiom of choice holds
\end{lemma}
\begin{proof}
  \todo{proof here}
\end{proof}

@@

Finally, we can get around the order requirement for prop-valued predicates for
omniscience.
\begin{lemma}
  Omniscience and exhaustibility coincide for prop-valued predicates.
\end{lemma}
\section{Countdown}
We have already introduced and described countdown: in this section, we will
fill in the remaining parts of the solver, glue the pieces together, and show
how the finiteness proofs can assist us to write the solver.
\subsection{Finite Permutations}
\subsection{Parenthesising}
\subsection{Filtering}
\subsection{Putting It All Together}
\section{Automating Proofs}
One use for above constructions is the automation of certain proofs.
In \cite{firsovDependentlyTypedProgramming2015}, which uses a similar approach
to ours, the \(\AgdaDatatype{Pauli}\) group is used as an example.
\ExecuteMetaData[agda/Data/Pauli.tex]{def}
As \(\AgdaDatatype{Pauli}\) has 4 constructors, \(n\)-ary functions on
\(\AgdaDatatype{Pauli}\) may require up to \(4^n\) cases, making even simple
proofs prohibitively verbose.
